\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-09-02 paper.tex
Added plot of croquignole expe
WIP on the Croquignole expe

\begin{figure}
        \centering
        \includegraphics[width=0.9\columnwidth]{ranger-side}
        \caption{Infants playing freely (!) with an EPFL's \emph{Ranger} robot.
        The behaviour of the robot is controlled with \pyRobots. It sustained an
        average of 70 actions triggered by minute over more than an hour,
        with peaks at 200 actions/minute.}
        \label{expe-nursery}
\end{figure}

>>>>

We organized in June 2014 a pilot study in a kindergarten (on campus) to
stress-test the hardware and software of the Ranger
robot~\cite{mondada2014ranger}. The Ranger robot is an autonomous robot designed
for interaction with children. As it was primarily designed to support children
with tidying up, it is shaped as a wooden ``box on wheels''
(Figure~\ref{expe-nursery}). Hardware-wise, it features an RGB-D camera, IR
sensors, a range and bearing sensor, a physical front bumper, a scale, a
removable pacifier (used as a soft on/off switch by the children) and it is
covered with capacitive tactile panels. The wooden panels cover 186 RGB LEDs,
enabling various light patterns, it can play sounds, the two eyes can be fully
controlled (2 DoFs pupils and actuated eye-lids). Wheel controllers are designed
such as they switch to freewheel as soon as the robot is pushed by the children.
The robot is powered by an embedded Gumstix Overo (ARM7l) board running a custom
Linux image, assisted by three custom microcontroller boards (for low-level
hardware interfacing).

Software-wise, all the user-facing behaviours are implemented with \pyRobots,
and the communication with the hardware is abstracted through a mix of ROS
and Aseba~\cite{magnenat2011aseba} nodes.

\begin{figure}
        \centering
        \includegraphics[width=0.9\columnwidth]{ranger-side}
        \caption{Infants playing freely (!) with an EPFL's \emph{Ranger} robot.
        The behaviour of the robot is controlled with \pyRobots.}
        \label{expe-nursery}
\end{figure}

We brought two Ranger robots to a kindergarten (17 children, 3 to 4 years old),
and after a brief introduction (showing them that removing the pacifier would
``wake up'' the robot, and putting it back would make it ``fall asleep''), we
invited the children to freely play with the robots and integrate them into
their usual games. The experiment lasted 68 minutes.

We purposefully designed a simple behavioural scheme
(Listing~\ref{croquignole_no_move}): two background actions
(\python|background_blink| and \python|look_at_touches|) run continuously, and 4
events are monitored (pacifier added/removed, toy added and bumper hit).

\begin{pythoncode}
    @action
    def on_pacifier(robot):
        robot.look_at_lolette()
        robot.blink()
        sleep = robot.fall_asleep()
        robot.lightbar(ramp=colors.RAINBOW).wait()
        sleep.wait()

    @action
    def on_pacifier_removed(robot):
        robot.light_bar(colors.from_hls(rand(0,1),0.8,1))
        robot.wakeup().wait()
        robot.move(0.4, v = 0.8).wait()
        robot.idle().wait()

    @action
    def on_bumper(robot):
        pulse = robot.pulse_row(0, (128, 0, 128))
        while abs(robot.state.v) > 0.01:
            robot.sleep(0.2)
        pulse.cancel()

    @action
    def on_toy(robot):
        robot.playsound(SOUNDS["toy_in"])
        robot.lightbar(ramp=colors.RAINBOW).wait()

    with Ranger() as robot:

        robot.background_blink()
        robot.look_at_touches()

        robot.every("pacifier", becomes = True).do(on_pacifier)
        robot.every("pacifier", becomes = False)
                                       .do(on_pacifier_removed)
        robot.every("scale", increase = 0.3).do(on_toy)
        robot.every("bumper", becomes = True).do(on_bumper)

        while True:
            time.sleep(0.1)
\end{pythoncode}
\caption{Source of the high-level behaviours running on the robots during the
nursery pilot (some behaviours like battery management have been omitted for
clarity).}
\label{croquignole_no_move}
\end{listing}

\begin{figure}
    \resizebox{\columnwidth}{!}{\input{croquignole-expe}}
    \caption{Events fired and actions started per minute, over the 68 min-long
    experiment. The robot sustains an average of 70 actions triggered by minute over
    more than an hour, with peaks at 200 actions/minute.}

\end{figure}
